---
title: "InterACT SR/OR data fitting"
output:
  html_document:
    code_folding: show
    df_print: kable
    fig_caption: yes
    highlight: tango
    number_sections: yes
    theme: paper
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}
library(knitr)
opts_chunk$set(tidy=TRUE, warning=FALSE, message=FALSE)
set.seed(4711)
library(tidyverse)
options(dplyr.width = Inf)
```


# Prepare model

## Load interAct
```{r }
source("interACT.R")
```

## Define model
> Interference model with 2 conditions: Target-match, distractor-match/mismatch

```{r model}
model_2cond <- list(
	target_match = list(c(1,1), c(1,1)),  ## codes trtmt and baseline conditions
	distractor_match = list(c(0,1), c(0,0)), ## trtmt 0,1 baseline 0,0
	Target = c("Match","Match"),
	Distractor = c("Match","Mismatch"),
	weights = list(c(strWeight(),semWeight()))
	)
```

## Set parameters
```{r params}
reset_params()
lf        <<- 0.15    # latency factor
rth 	    <<- -1.5    # retrieval threshold
bll       <<- 0.5     # decay parameter
ans       <<- 0.2     # activation noise
mas       <<- 1.5       # maximum associative strength 
mp        <<- 1       # mismatch penalty
ga        <<- 0       # goal source activation
blc       <<- 0       # target base-level activation
lp        <<- 1       # target time since last presentation (msec)
ldp       <<- 1       # last distractor presentation (msec)
## Distractor control:
ndistr    <<- 1				# number of distractors
dbl       <<- 0       # distractor base-level
```

### Optional model extensions
> Quality correction factor *qcf*: When $qcf > 0$, base-level influences match-quality (and thus the fan)  
> Prominence scaling constant *psc*: When $psc > 0$, prominence influences base-level activation  

```{r params1}
psc <<- 1 
qcf <<- 1
cuesim <<- -1         # Cue-feature similarity [-1..0]
dprom <<- 0  				  # Distractor prominence
cueweighting <<- 1    # Strength of structural cue as ratio   
```



## Test run model with parameter range

```{r parmrange1}
lf <<- seq(0.1,0.4, by = .1)
mas <<- c(1)
ans <<- seq(0.2,0.7, by = .1)
ga <<- c(0.2, 0.6, 1)
```

```{r run}
sims <- create_param_matrix(model_2cond, iterations=2000)
(n_sims <- nrow(sims))

results <- run(sims)

means <- results %>% group_by(Set, Condition) %>% summarise(Mean = mean(acc))
summary(means$Mean)
head(means)
params <- select(sims, Set, lf:weights) %>% distinct()
head(params)
```



# Fit data

## Load data

```{r loaddata}
load("subjaccRC.Rda")
head(subjaccRC)
str(subjaccRC)
```

## Define a fitting function
```{r fitfunction}
dofit <- function(dat, model, n = 1000){
	datdf <- data.frame(ID = dat[3], Condition = c(2,1), Data = as.numeric(dat[1:2]))
	print(datdf)

	# Run model
	sims <- create_param_matrix(model, n)
	results <- run(sims)

	means <- results %>% group_by(Set, Condition) %>% summarise(Model = mean(acc))
	means <- left_join(means, datdf)

	# Numerical fit
	means <- mutate(means, d=abs(Data-Model))
	# Summarise numerical fit and correlation
	fit <- means %>% group_by(Set) %>% 
		summarise(
			rmsd=mean(d, na.rm=TRUE), 
			SE=sd(d)/sqrt(n()), 
			R=cor(Model, Data)
		)
	fit$R[is.na(fit$R)] <- 1

	# Select best fit
	bestfit <- filter(fit, rmsd == min(rmsd))

	# Return data
	params <- select(sims, Set, lf:weights) %>% distinct()
	bestmodel <- filter(means, Set%in%bestfit$Set) %>% left_join(bestfit) %>% left_join(params)
	bestmodel <- bestmodel %>% gather(Dataset, Mean, Model, Data)
	bestmodel
}
```

## Fit data

```{r paramsforfit}
lf <<- seq(0.1,0.4, by = .1)
mas <<- c(1)
ans <<- seq(0.2,0.7, by = .1)
ga <<- c(0.2, 0.6, 1)
```

```{r fit, results='hide'}
subjaccRC <- as.data.frame(subjaccRC)
subjaccRC$ID <- rownames(subjaccRC)

res <- apply(subjaccRC, 1, dofit, model_2cond, 2000)
```

```{r fitres}
allresults <- bind_rows(res)
allresults <- allresults %>% mutate(Condition = ifelse(Condition==1, "SS","SO"))
head(allresults)

# ggplot(filter(allresults), aes(Condition, Mean, color=Dataset, group=Dataset)) +
# 	geom_point() +
# 	geom_line() +
# 	facet_wrap(~ID)
```


